Cell Type Specific Validation

### 2019-07-12 Scripts/comparing_tfbs_specific_models_with_all_annotations.Rmd
added 5kb results

@@

for(i in paste0("CHR", c(1:8,10:22))){
	for(j in c("chromstates", "histones", "tfbs", "all")){
	  if(j %in% c("chromstates", "histones", "tfbs")){
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_",
									   j, 
									   ".rds"))
	  }else{
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf.rds"))
	  }

@@

for(i in paste0("CHR", c(1:8,10:22))){
	for(j in c("chromstates", "histones", "tfbs", "all")){
	  if(j %in% c("chromstates", "histones", "tfbs")){
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_",
									   j, 
									   ".rds"))
	  }else{
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf.rds"))
	  }

@@

for(i in paste0("CHR", c(1:8,10:22))){
	for(j in c("chromstates", "histones", "tfbs", "all")){
	  if(j %in% c("chromstates", "histones", "tfbs")){
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_",
									   j, 
									   ".rds"))
	  }else{
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf.rds"))
	  }

@@

for(i in paste0("CHR", c(1:8,10:22))){
	for(j in c("chromstates", "histones", "tfbs", "all")){
	  if(j %in% c("chromstates", "histones", "tfbs")){
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/100kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_",
									   j, 
									   ".rds"))
	  }else{
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/100kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf.rds"))
	  }

@@

@@

for(i in paste0("CHR", c(1:8,10:22))){
	for(j in c("chromstates", "histones", "tfbs", "all")){
	  if(j %in% c("chromstates", "histones", "tfbs")){
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_",
									   j, 
									   ".rds"))
	  }else{
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf.rds"))
	  }

@@

for(i in paste0("CHR", c(1:8,10:22))){
	for(j in c("chromstates", "histones", "tfbs", "all")){
	  if(j %in% c("chromstates", "histones", "tfbs")){
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/25kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_",
									   j, 
									   ".rds"))
	  }else{
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/25kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf.rds"))
	  }

@@

for(i in paste0("CHR", c(1:8,10:22))){
	for(j in c("chromstates", "histones", "tfbs", "all")){
	  if(j %in% c("chromstates", "histones", "tfbs")){
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/50kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_",
									   j, 
									   ".rds"))
	  }else{
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/50kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf.rds"))
	  }

@@

for(i in paste0("CHR", c(1:8,10:22))){
	for(j in c("chromstates", "histones", "tfbs", "all")){
	  if(j %in% c("chromstates", "histones", "tfbs")){
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/100kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_",
									   j, 
									   ".rds"))
	  }else{
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/100kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf.rds"))
	  }

@@

```{r}
all_rfperfs <- rbind.data.frame(mccdata_gm12878_10kb,
                                mccdata_gm12878_25kb,
                                mccdata_gm12878_50kb,
                                mccdata_gm12878_100kb,
                                mccdata_K562_10kb,
                                mccdata_K562_25kb,
                                mccdata_K562_50kb,
                                mccdata_K562_100kb)
all_rfperfs$CL <- c(rep("GM12878", length(mccdata_gm12878_10kb)*4), rep("K562", length(mccdata_K562_10kb)*4))
all_rfperfs$Resolution <- rep(c(rep("10 kb", 84),
                            rep("25 kb", 84),
                            rep("50 kb", 84),
                            rep("100 kb", 84)))
all_rfperfs$Annotation <- rep(c("CSS","HM","TFBS","Combined"),168)
all_rfperfs$Chromosome <- rep(c(rep("CHR1", 4),
                            rep("CHR2", 4),
                            rep("CHR3", 4),
                            rep("CHR4", 4),
                            rep("CHR5", 4),
                            rep("CHR6", 4),
                            rep("CHR7", 4),
                            rep("CHR8", 4),
                            rep("CHR10", 4),
                            rep("CHR11", 4),
                            rep("CHR12", 4),
                            rep("CHR13", 4),
                            rep("CHR14", 4),
                            rep("CHR15", 4),
                            rep("CHR16", 4),
                            rep("CHR17", 4),
                            rep("CHR18", 4),
                            rep("CHR19", 4),
                            rep("CHR20", 4),
                            rep("CHR21", 4),
                            rep("CHR22", 4)),8)

all_rfperfs$CL <- factor(all_rfperfs$CL, levels = c("GM12878", "K562"))
all_rfperfs$Resolution <- factor(all_rfperfs$Resolution, levels = c("10 kb", "25 kb", "50 kb", "100 kb"))
all_rfperfs$Annotation <- factor(all_rfperfs$Annotation, levels = c("HM", "CSS", "TFBS", "Combined"))
all_rfperfs$Chromosome <- factor(all_rfperfs$Chromosome, levels = paste0("CHR", c(1:8,10:22)))

>>>>

## 5kb

```{r}
mccdata_gm12878_5kb <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
	for(j in c("chromstates", "histones", "tfbs", "all")){
	  if(j %in% c("chromstates", "histones", "tfbs")){
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_",
									   j, 
									   ".rds"))
	  }else{
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_noenet.rds"))
	  }

			mccdata_gm12878_5kb <- rbind(mccdata_gm12878_5kb,
										  perfdata[15,2])

@@

for(i in paste0("CHR", c(1:8,10:22))){
	for(j in c("chromstates", "histones", "tfbs", "all")){
	  if(j %in% c("chromstates", "histones", "tfbs")){
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_",
									   j, 
									   ".rds"))
	  }else{
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_noenet.rds"))
	  }

@@

for(i in paste0("CHR", c(1:8,10:22))){
	for(j in c("chromstates", "histones", "tfbs", "all")){
	  if(j %in% c("chromstates", "histones", "tfbs")){
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_",
									   j, 
									   ".rds"))
	  }else{
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_noenet.rds"))
	  }

@@

for(i in paste0("CHR", c(1:8,10:22))){
	for(j in c("chromstates", "histones", "tfbs", "all")){
	  if(j %in% c("chromstates", "histones", "tfbs")){
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_",
									   j, 
									   ".rds"))
	  }else{
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_noenet.rds"))
	  }

@@

for(i in paste0("CHR", c(1:8,10:22))){
	for(j in c("chromstates", "histones", "tfbs", "all")){
	  if(j %in% c("chromstates", "histones", "tfbs")){
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/100kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_",
									   j, 
									   ".rds"))
	  }else{
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/100kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_noenet.rds"))
	  }

@@

## 5kb

```{r}
mccdata_K562_5kb <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
	for(j in c("chromstates", "histones", "tfbs", "all")){
	  if(j %in% c("chromstates", "histones", "tfbs")){
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_",
									   j, 
									   ".rds"))
	  }else{
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_noenet.rds"))
	  }

			mccdata_K562_5kb <- rbind(mccdata_K562_5kb,
										  perfdata[15,2])

@@

for(i in paste0("CHR", c(1:8,10:22))){
	for(j in c("chromstates", "histones", "tfbs", "all")){
	  if(j %in% c("chromstates", "histones", "tfbs")){
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_",
									   j, 
									   ".rds"))
	  }else{
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_noenet.rds"))
	  }

@@

for(i in paste0("CHR", c(1:8,10:22))){
	for(j in c("chromstates", "histones", "tfbs", "all")){
	  if(j %in% c("chromstates", "histones", "tfbs")){
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/25kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_",
									   j, 
									   ".rds"))
	  }else{
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/25kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_noenet.rds"))
	  }

@@

for(i in paste0("CHR", c(1:8,10:22))){
	for(j in c("chromstates", "histones", "tfbs", "all")){
	  if(j %in% c("chromstates", "histones", "tfbs")){
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/50kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_",
									   j, 
									   ".rds"))
	  }else{
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/50kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_noenet.rds"))
	  }

@@

for(i in paste0("CHR", c(1:8,10:22))){
	for(j in c("chromstates", "histones", "tfbs", "all")){
	  if(j %in% c("chromstates", "histones", "tfbs")){
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/100kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_",
									   j, 
									   ".rds"))
	  }else{
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/100kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_noenet.rds"))
	  }

@@

```{r}
all_rfperfs <- rbind.data.frame(mccdata_gm12878_5kb,
                                mccdata_gm12878_10kb,
                                mccdata_gm12878_25kb,
                                mccdata_gm12878_50kb,
                                mccdata_gm12878_100kb,
                                mccdata_K562_5kb,
                                mccdata_K562_10kb,
                                mccdata_K562_25kb,
                                mccdata_K562_50kb,
                                mccdata_K562_100kb)
all_rfperfs$CL <- c(rep("GM12878", length(mccdata_gm12878_5kb)*5), rep("K562", length(mccdata_K562_5kb)*5))
all_rfperfs$Resolution <- c(rep("5 kb", length(mccdata_gm12878_5kb)),
                            rep("10 kb", length(mccdata_gm12878_10kb)),
                            rep("25 kb", length(mccdata_gm12878_25kb)),
                            rep("50 kb", length(mccdata_gm12878_50kb)),
                            rep("100 kb", length(mccdata_gm12878_100kb)))
all_rfperfs$Annotation <- rep(c("CSS","HM","TFBS","Combined"),210)
all_rfperfs$Chromosome <- rep(c(rep("CHR1", 4),
                            rep("CHR2", 4),
                            rep("CHR3", 4),
                            rep("CHR4", 4),
                            rep("CHR5", 4),
                            rep("CHR6", 4),
                            rep("CHR7", 4),
                            rep("CHR8", 4),
                            rep("CHR10", 4),
                            rep("CHR11", 4),
                            rep("CHR12", 4),
                            rep("CHR13", 4),
                            rep("CHR14", 4),
                            rep("CHR15", 4),
                            rep("CHR16", 4),
                            rep("CHR17", 4),
                            rep("CHR18", 4),
                            rep("CHR19", 4),
                            rep("CHR20", 4),
                            rep("CHR21", 4),
                            rep("CHR22", 4)),10)

all_rfperfs$CL <- factor(all_rfperfs$CL, levels = c("GM12878", "K562"))
all_rfperfs$Resolution <- factor(all_rfperfs$Resolution, levels = c("5 kb", "10 kb", "25 kb", "50 kb", "100 kb"))
all_rfperfs$Annotation <- factor(all_rfperfs$Annotation, levels = c("HM", "CSS", "TFBS", "Combined"))
all_rfperfs$Chromosome <- factor(all_rfperfs$Chromosome, levels = paste0("CHR", c(1:8,10:22)))

### 2019-07-12 Scripts/evaluating_cell_line_specific_validation_performances.Rmd
added 5kb results

@@

@@

@@

@@

```{r}
all_rfperfs_cl_specific_valid <- rbind.data.frame(mccdata_gm12878_on_k562_10kb,
                                                  mccdata_gm12878_on_k562_25kb,
                                                  mccdata_gm12878_on_k562_50kb,
                                                  mccdata_gm12878_on_k562_100kb,
                                                  mccdata_k562_on_gm12878_10kb,
                                                  mccdata_k562_on_gm12878_25kb,
                                                  mccdata_k562_on_gm12878_50kb,
                                                  mccdata_k562_on_gm12878_100kb,
                                                  mccdata_gm12878_on_gm12878_10kb,
                                                  mccdata_gm12878_on_gm12878_25kb,
                                                  mccdata_gm12878_on_gm12878_50kb,
                                                  mccdata_gm12878_on_gm12878_100kb,
                                                  mccdata_k562_on_k562_10kb,
                                                  mccdata_k562_on_k562_25kb,
                                                  mccdata_k562_on_k562_50kb,
                                                  mccdata_k562_on_k562_100kb)

all_rfperfs_cl_specific_valid$Chromosome <- rep(c("CHR1",
                                                  "CHR2",
                                                  "CHR3",
                                                  "CHR4",
                                                  "CHR5",
                                                  "CHR6",
                                                  "CHR7",
                                                  "CHR8",
                                                  "CHR10",
                                                  "CHR11",
                                                  "CHR12",
                                                  "CHR13",
                                                  "CHR14",
                                                  "CHR15",
                                                  "CHR16",
                                                  "CHR17",
                                                  "CHR18",
                                                  "CHR19",
                                                  "CHR20",
                                                  "CHR21",
                                                  "CHR22"),16)
all_rfperfs_cl_specific_valid$Resolution <- rep(c(rep("10 kb", 21),
                                              rep("25 kb", 21),
                                              rep("50 kb", 21),
                                              rep("100 kb", 21)), 4)
all_rfperfs_cl_specific_valid$Validation <- c(rep("GM12878 on K562", 21*4),
                                              rep("K562 on GM12878", 21*4),
                                              rep("GM12878 on GM12878", 21*4),
                                              rep("K562 on K562", 21*4))

all_rfperfs_cl_specific_valid$Validation <- factor(all_rfperfs_cl_specific_valid$Validation, levels = c("GM12878 on GM12878", "K562 on K562", "GM12878 on K562", "K562 on GM12878"))
all_rfperfs_cl_specific_valid$Resolution <- factor(all_rfperfs_cl_specific_valid$Resolution, levels = c("10 kb", "25 kb", "50 kb", "100 kb"))
all_rfperfs_cl_specific_valid$Chromosome <- factor(all_rfperfs_cl_specific_valid$Chromosome, levels = paste0("CHR", c(1:8,10:22)))

>>>>

### 5kb

```{r}
mccdata_gm12878_on_k562_5kb <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
			files <- list.files(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/"))
		  if("rfperf_tfbs_GM12878_on_K562.rds" %in% files){
		    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_tfbs_GM12878_on_K562.rds"))
		  }else{perfdata=data.frame(Metric = c("TN",
                                "FN",
                                "FP",
                                "TP",
                                "Total",
                                "Sensitivity",
                                "Specificity",
                                "Kappa",
                                "Accuracy",
                                "Precision",
                                "FPR",
                                "FNR",
                                "FOR",
                                "NPV",
                                "MCC",
                                "F1",
                                "AUC",
                                "Youden",
                                "AUPRC"), 
                     Performance=NA)}

			mccdata_gm12878_on_k562_5kb <- rbind(mccdata_gm12878_on_k562_5kb,
			                                      perfdata[15,2])
}

@@

### 5kb

```{r}
mccdata_k562_on_gm12878_5kb <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
			files <- list.files(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/"))
		  if("rfperf_tfbs_K562_on_GM12878.rds" %in% files){
		    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_tfbs_K562_on_GM12878.rds"))
		  }else{perfdata=data.frame(Metric = c("TN",
                                "FN",
                                "FP",
                                "TP",
                                "Total",
                                "Sensitivity",
                                "Specificity",
                                "Kappa",
                                "Accuracy",
                                "Precision",
                                "FPR",
                                "FNR",
                                "FOR",
                                "NPV",
                                "MCC",
                                "F1",
                                "AUC",
                                "Youden",
                                "AUPRC"), 
                     Performance=NA)}

			mccdata_k562_on_gm12878_5kb <- rbind(mccdata_k562_on_gm12878_5kb,
			                                      perfdata[15,2])
}

@@

### 5kb

```{r}
mccdata_gm12878_on_gm12878_5kb <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
			files <- list.files(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/"))
		  if("rfperf_tfbs.rds" %in% files){
		    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_tfbs.rds"))
		  }else{perfdata=data.frame(Metric = c("TN",
                                "FN",
                                "FP",
                                "TP",
                                "Total",
                                "Sensitivity",
                                "Specificity",
                                "Kappa",
                                "Accuracy",
                                "Precision",
                                "FPR",
                                "FNR",
                                "FOR",
                                "NPV",
                                "MCC",
                                "F1",
                                "AUC",
                                "Youden",
                                "AUPRC"), 
                     Performance=NA)}

			mccdata_gm12878_on_gm12878_5kb <- rbind(mccdata_gm12878_on_gm12878_5kb,
			                                      perfdata[15,2])
}

@@

### 5kb

```{r}
mccdata_k562_on_k562_5kb <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
			files <- list.files(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/"))
		  if("rfperf_tfbs.rds" %in% files){
		    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_tfbs.rds"))
		  }else{perfdata=data.frame(Metric = c("TN",
                                "FN",
                                "FP",
                                "TP",
                                "Total",
                                "Sensitivity",
                                "Specificity",
                                "Kappa",
                                "Accuracy",
                                "Precision",
                                "FPR",
                                "FNR",
                                "FOR",
                                "NPV",
                                "MCC",
                                "F1",
                                "AUC",
                                "Youden",
                                "AUPRC"), 
                     Performance=NA)}

			mccdata_k562_on_k562_5kb <- rbind(mccdata_k562_on_k562_5kb,
			                                      perfdata[15,2])
}

@@

```{r}
all_rfperfs_cl_specific_valid <- rbind.data.frame(mccdata_gm12878_on_k562_5kb,
                                                  mccdata_gm12878_on_k562_10kb,
                                                  mccdata_gm12878_on_k562_25kb,
                                                  mccdata_gm12878_on_k562_50kb,
                                                  mccdata_gm12878_on_k562_100kb,
                                                  mccdata_k562_on_gm12878_5kb,
                                                  mccdata_k562_on_gm12878_10kb,
                                                  mccdata_k562_on_gm12878_25kb,
                                                  mccdata_k562_on_gm12878_50kb,
                                                  mccdata_k562_on_gm12878_100kb,
                                                  mccdata_gm12878_on_gm12878_5kb,
                                                  mccdata_gm12878_on_gm12878_10kb,
                                                  mccdata_gm12878_on_gm12878_25kb,
                                                  mccdata_gm12878_on_gm12878_50kb,
                                                  mccdata_gm12878_on_gm12878_100kb,
                                                  mccdata_k562_on_k562_5kb,
                                                  mccdata_k562_on_k562_10kb,
                                                  mccdata_k562_on_k562_25kb,
                                                  mccdata_k562_on_k562_50kb,
                                                  mccdata_k562_on_k562_100kb)

all_rfperfs_cl_specific_valid$Chromosome <- rep(c("CHR1",
                                                  "CHR2",
                                                  "CHR3",
                                                  "CHR4",
                                                  "CHR5",
                                                  "CHR6",
                                                  "CHR7",
                                                  "CHR8",
                                                  "CHR10",
                                                  "CHR11",
                                                  "CHR12",
                                                  "CHR13",
                                                  "CHR14",
                                                  "CHR15",
                                                  "CHR16",
                                                  "CHR17",
                                                  "CHR18",
                                                  "CHR19",
                                                  "CHR20",
                                                  "CHR21",
                                                  "CHR22"),20)
all_rfperfs_cl_specific_valid$Resolution <- rep(c(rep("5 kb", 21),
                                              rep("10 kb", 21),
                                              rep("25 kb", 21),
                                              rep("50 kb", 21),
                                              rep("100 kb", 21)), 4)
all_rfperfs_cl_specific_valid$Validation <- c(rep("GM12878 on K562", 21*5),
                                              rep("K562 on GM12878", 21*5),
                                              rep("GM12878 on GM12878", 21*5),
                                              rep("K562 on K562", 21*5))

all_rfperfs_cl_specific_valid$Validation <- factor(all_rfperfs_cl_specific_valid$Validation, levels = c("GM12878 on GM12878", "K562 on K562", "GM12878 on K562", "K562 on GM12878"))
all_rfperfs_cl_specific_valid$Resolution <- factor(all_rfperfs_cl_specific_valid$Resolution, levels = c("5 kb", "10 kb", "25 kb", "50 kb", "100 kb"))
all_rfperfs_cl_specific_valid$Chromosome <- factor(all_rfperfs_cl_specific_valid$Chromosome, levels = paste0("CHR", c(1:8,10:22)))
